\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
    pdftitle={Academic Report - Computer Science Lab Portfolio},
}

\title{\textbf{Academic Report: Technical Portfolio Architecture and Job Alignment}}
\author{\textbf{Aiman Mamad Hussen} \\ B.Sc. Computer Science \\ GISMA University of Applied Sciences}
\date{June 2026}

\begin{document}

\maketitle

\section{Introduction}
This academic report documents the successful architecture, implementation, and deployment of a professional technical portfolio developed as a core requirement of the Computer Science Lab curriculum. In the modern software engineering and information technology sectors, maintaining a version-controlled, publicly accessible repository of technical artifacts is standard practice for professional transparency and verification of competencies. 

The primary purpose of this project is to build a centralized deployment environment utilizing industry-standard technologies to showcase academic outputs, foundational programming tasks, and ongoing technological projects. This report demonstrates version control proficiency, infrastructure hosting via cloud platforms, basic front-end development, and direct professional alignment with target opportunities within the German tech infrastructure.

\section{Methodology and Technical Tools}
The implementation of the portfolio relied entirely on industry-proven tools to ensure compliance with professional standard operating procedures in software documentation:
\begin{itemize}[noitemsep]
    \item \textbf{LaTeX (Overleaf Platform):} Selected for typesetting both the Curriculum Vitae and this formal report. LaTeX provides a compilation framework that separates layout design from content compilation, yielding mathematically precise layouts superior to standard text processors.
    \item \textbf{GitHub (Git Version Control):} Used as the core remote repository to track code mutations, manage branches, and maintain absolute source integrity.
    \item \textbf{HTML \& CSS:} Employed to code a responsive, accessible, dark-themed static interface optimized for fast rendering speeds across distinct device nodes.
    \item \textbf{GitHub Pages Engine:} Utilized as a serverless static hosting solution, mapping compiled production code directly from the main repository branch to a live web-accessible domain.
\end{itemize}

\section{Target Student Job Alignment and Professional Synergy}
Connecting academic assignments with live industrial vacancies ensures operational readiness. For this laboratory validation, an active technical student worker position was selected within the automotive and software engineering sector.

\begin{itemize}
    \item \textbf{Company:} Mercedes-Benz AG
    \item \textbf{Position Title:} Werkstudentin/Werkstudent Programmierung \& Monitoring / Analysedashboards für Fahrzeukinbetriebnahme (Hybrid Working Node / Bremen)
    \item \textbf{Official Checked Vacancy URL:} \\
    \url{https://www.stepstone.de/stellenangebote--Werkstudentin-Programmierung-Monitoring-Analysedashboards-fuer-Fahrzeukinbetriebnahme-Bremen-Mercedes-Benz-AG--14098504-inline.html}
\end{itemize}

This vacancy at Mercedes-Benz AG matches my personal background and my current studies perfectly for three main reasons:
\begin{enumerate}
    \item \textbf{Automotive Background:} The job is focused on vehicle software commissioning (\textit{Fahrzeukinbetriebnahme}). Since I have practical experience working as a mechanic, I already understand how cars and automotive workshop environments work. This hands-on experience is a big advantage when working with software deployed directly into physical vehicles.
    \item \textbf{Management Skills:} My previous job in the hotel sector taught me a lot about management, daily operations, and how to stay organized. These management skills are directly useful for tracking tasks and organizing the data monitoring workflows that this department requires.
    \item \textbf{Computer Science Studies:} As a B.Sc. Computer Science student, I am learning the exact technical skills needed to program data tools and analytical dashboards. Combining my practical experience in mechanics and management with my current IT studies creates the right profile for a position that bridges hardware and software infrastructure.
\end{enumerate}

\section{Centralized Repository Architecture and Asset Indexes}
To fulfill the evaluation criteria defined by the laboratory director, all production files, layout source codes, and rendered outputs have been integrated into a public repository. The production layer is configured to pull updates immediately upon code synchronization.

The underlying project infrastructure, containing all verified hyperlinks embedded within the static portfolio view, is indexed via the hyperlinks below:

\begin{itemize}
    \item \textbf{Live Portfolio Interface URL:} \href{https://aiman-hussen.github.io/}{https://aiman-hussen.github.io/}
    \item \textbf{Root Git Source Repository:} \href{https://github.com/Aiman-Hussen/Aiman-Hussen.github.io}{github.com/Aiman-Hussen/Aiman-Hussen.github.io}
    \item \textbf{Compiled Curriculum Vitae Asset (PDF):} \href{https://aiman-hussen.github.io/main.pdf}{aiman-hussen.github.io/main.pdf}
    \item \textbf{Curriculum Vitae Source Hierarchy (.tex):} \href{https://aiman-hussen.github.io/main.tex}{aiman-hussen.github.io/main.tex}
\end{itemize}

\section{Conclusion and Future Iterations}
The execution of this lab deployment confirms the practical application of software delivery frameworks. The portfolio is architected as a dynamic ecosystem; while it currently hosts foundational technical artifacts (the professional resume and this initial job alignment report), the interface contains modular sections designed to incorporate upcoming semester deliverables, object-oriented programming tasks, and engine-specific software prototypes. Linking academic validation to an enterprise node like Mercedes-Benz AG provides a standardized pathway for regional job integration.

\end{document}